### 2015-04-21 paper.tex
Change hyperref parameters
Change tense of 'indicated'

% Use nameref to cite supporting information files (see Supporting Information
% section for more info)
\usepackage{nameref,hyperref}

@@

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicated that the RM2 blades are operating further from
stall---consistent with the higher tip speed ratio operation.

>>>>

% Use nameref to cite supporting information files (see Supporting Information
% section for more info)
\usepackage{nameref}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

@@

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicates that the RM2 blades are operating further from
stall---consistent with the higher tip speed ratio operation.
